\artus -- Framework for Event-based Data Analysis in High Energy Physics

### 2015-09-09 Core/doc/latex/paper.tex
on Artus

Following the structure of the CMSSW framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/\artus}} provides a front-to-end solution for the analysis of event-based data. The basic concept of modules processing the events within an event loop is complemented by tools for the configuration of every step. The complete structure is explained in the next section~\ref{section_artus_structure}.

This general framework is applicable to any kind of event processing analysis. The well-tested core is shared among various analyses, providing a reliable fundament for any new analysis. The highly modular structure guides the user to develop analysis software that is easily maintainable and constructively extensible. Thus, thes \artus framework avoids the aforementioned problems of separate user code for individual analyses.

@@

>>>>

Following the structure of the CMSSW \todo{Referenz? zumindest github-link?} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/\artus}} provides a front-to-end solution for the analysis of event-based data. The basic concept of modules processing the events within an event loop is complemented by tools for the configuration of every step. The complete structure is explained in the next section~\ref{section_artus_structure}.

This general framework is applicable to any kind of event processing analysis. The well-tested core is shared among various analyses, providing a reliable fundament for any new analysis. The highly modular structure guides the user to develop analysis software that is easily maintainable and constructively extensible. Thus, the \artus framework avoids the aforementioned problems of separate user code for individual analyses.

@@

\artus has no need to use multi-core techniques, since it can be parallelized trivially by splitting the input dataset and sending it to different computing instances. This is possible, because the processed events are know to be independent of each other.
